Model LF

### 2022-12-09 Power point test.Rmd
Commit

   nben_h_rest = TIMESERIES(c(nben_h_rest_obs),   
                       START=c(2005,2),FREQ=4),
  nben_h_un = TIMESERIES(c(nben_h_un_obs),   
                        START=c(2005,2),FREQ=4),
  komp_r = TIMESERIES(c(komp_r_obs1),   
                        START=c(2005,2),FREQ=4),
  shock = TIMESERIES(c(shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  stat_reg_shock = TIMESERIES(c(stat_reg_shock),   
                        START=c(2005,2),FREQ=4),

@@

```{r}
###Gengivelse af stød til model
max_dp_bs2 = Shock_bs2$simulation$max_dp
wage_bs2 = Shock_bs2$simulation$wage
komp_r_bs2 = Shock_bs2$simulation$komp_r
part_bs2 = Shock_bs2$simulation$part
yk_ds_bs2 = Shock_bs2$simulation$yk_ds
pc_ds_bs2 = Shock_bs2$simulation$pc_ds
wage_ds_t_bs2 = Shock_bs2$simulation$wage_ds_t
ur_ds_bs2 = Shock_bs2$simulation$ur_ds
emp_bs2 = Shock_bs2$simulation$emp
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
pconk_ds_bs2= Shock_bs2$simulation$pconk_ds
tilpas_pr_bs2 = Shock_bs2$simulation$tilpas_pr
u_ds_bs2 = Shock_bs2$simulation$u_ds
part_bs2 = Shock_bs2$simulation$part
nben_h_bs2 = Shock_bs2$simulation$nben_h
wage_ds_bs2 = Shock_bs2$simulation$wage_ds
dp_person_bs2 = Shock_bs2$simulation$dp_person
kont_h_ratio_bs2 = Shock_bs2$simulation$kont_h_ratio
unemp_bs2 = Shock_bs2$simulation$unemp
nl_g_bs2 = Shock_bs2$simulation$nl_g
inflation_bs2 = Shock_bs2$simulation$inflation
lf_bs2 = Shock_bs2$simulation$lf
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
wage_gap1_bs2 = Shock_bs2$simulation$wage_gap1
wage_gap_bs2 = Shock_bs2$simulation$wage_gap
prod_bs2 = Shock_bs2$simulation$prod
prod_bs2 = Shock_bs2$simulation$prod
ws_bs2 = Shock_bs2$simulation$ws
xk_ds_bs2 = Shock_bs2$simulation$xk_ds
mk_ds_bs2 = Shock_bs2$simulation$mk_ds

net_balance_bs2 = xk_ds_bs2 - mk_ds_bs2
net_balance_bs2_ratio= (xk_ds_bs2 - mk_ds_bs2)/yk_ds_bs2

@@

ik_ratio_bs2 = ik_bs2/yk_ds_bs2
mk_ratio_bs2 = mk_bs2/yk_ds_bs2

c_ratio_bs2 = pconk_ds_bs2/yk_ds_bs2
```

```{r}
plot(wage_ds_t_bs2, col= "black", xlab= "Year", ylab= "% Change in wages", main= "Wages");
lines(wage_ds_t, col="red")
grid()
```

@@

yk_ds_02 = Shock_2$simulation$yk_ds
emp_02 = Shock_2$simulation$emp
wage_ds_02 = Shock_2$simulation$wage_ds
ur_ds_02 = Shock_2$simulation$ur_ds
pc_ds_02 = Shock_2$simulation$pc_ds
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
pconk_ds_02 = Shock_2$simulation$pconk_ds
komp_r_02 = Shock_2$simulation$komp_r
max_dp_02 = Shock_2$simulation$max_dp
nben_h_02 = Shock_2$simulation$nben_h
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
ik_02 = Shock_2$simulation$ik
wage_ds_t_02 = Shock_2$simulation$wage_ds_t
nben_h_un_02 = Shock_2$simulation$nben_h_un
nl_g_02 = Shock_2$simulation$nl_g
nsben_h_02 = Shock_2$simulation$nsben_h
dp_person_02 = Shock_2$simulation$dp_person
xk_ds_02 = Shock_2$simulation$xk_ds
mk_ds_02 = Shock_2$simulation$mk_ds
ik_02 = Shock_2$simulation$ik
rer_02 = Shock_2$simulation$rer
ps_ds_02 = Shock_2$simulation$ps_ds
i_bd_nfc_k_ds_02 = Shock_2$simulation$i_bd_nfc_k_ds
yd1_hk_ds_02 = Shock_2$simulation$yd1_hk_ds
yd2a_hk_ds_02 = Shock_2$simulation$yd2a_hk_ds
yd2b_hk_02 = Shock_2$simulation$yd2b_hk
i_equip_nfc_k_ds_02 = Shock_2$simulation$i_equip_nfc_k_ds
u_ds_02 = Shock_2$simulation$u_ds
wage_gap1_02 = Shock_2$simulation$wage_gap1
gk_02 = Shock_2$simulation$gk
kont_h_ratio_02 = Shock_2$simulation$kont_h_ratio
lf_02 = Shock_2$simulation$lf
wage_gap_02 = Shock_2$simulation$wage_gap
max_gap_02 = Shock_2$simulation$max_gap
unemp_02 = Shock_2$simulation$unemp
inflation_02 = Shock_2$simulation$inflation
prod_02 = Shock_2$simulation$prod
ws_02 = Shock_2$simulation$ws
net_balance_02 = xk_ds_02 - mk_ds_02
```

plot(wage_gap1_bs2, col= "black", xlab= "Year", ylab= "Wage gap (ratio)", main= "Wage Gap in baseline");
lines(wage_gap1_00, col= "red");
grid()

plot(wage_ds_bs2, col= "black", xlab= "Year", ylab= "Wages (level)", main= "Wages in baseline");
lines(wage_ds_00, col= "red");
grid()

@@

>>>>

   nben_h_rest = TIMESERIES(c(nben_h_rest_obs),   
                       START=c(2005,2),FREQ=4),
  nben_h_un = TIMESERIES(c(nben_h_un_obs),   
                        START=c(2005,2),FREQ=4),
  komp_r = TIMESERIES(c(komp_r_obs1),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  stat_reg_shock = TIMESERIES(c(stat_reg_shock),   
                        START=c(2005,2),FREQ=4),

@@

```{r}
###Gengivelse af stød til model
max_dp_bs2 = Shock_bs2$simulation$max_dp
wage_bs2 = Shock_bs2$simulation$wage
komp_r_bs2 = Shock_bs2$simulation$komp_r
part_bs2 = Shock_bs2$simulation$part
yk_ds_bs2 = Shock_bs2$simulation$yk_ds
pc_ds_bs2 = Shock_bs2$simulation$pc_ds
wage_ds_t_bs2 = Shock_bs2$simulation$wage_ds_t
ur_ds_bs2 = Shock_bs2$simulation$ur_ds
emp_bs2 = Shock_bs2$simulation$emp
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
pconk_ds_bs2= Shock_bs2$simulation$pconk_ds
tilpas_pr_bs2 = Shock_bs2$simulation$tilpas_pr
u_ds_bs2 = Shock_bs2$simulation$u_ds
part_bs2 = Shock_bs2$simulation$part
nben_h_bs2 = Shock_bs2$simulation$nben_h
wage_ds_bs2 = Shock_bs2$simulation$wage_ds
dp_person_bs2 = Shock_bs2$simulation$dp_person
kont_h_ratio_bs2 = Shock_bs2$simulation$kont_h_ratio
unemp_bs2 = Shock_bs2$simulation$unemp
nl_g_bs2 = Shock_bs2$simulation$nl_g
inflation_bs2 = Shock_bs2$simulation$inflation
lf_bs2 = Shock_bs2$simulation$lf
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
wage_gap1_bs2 = Shock_bs2$simulation$wage_gap1
wage_gap_bs2 = Shock_bs2$simulation$wage_gap
prod_bs2 = Shock_bs2$simulation$prod
prod_bs2 = Shock_bs2$simulation$prod
ws_bs2 = Shock_bs2$simulation$ws
xk_ds_bs2 = Shock_bs2$simulation$xk_ds
mk_ds_bs2 = Shock_bs2$simulation$mk_ds
wage_ds_t_00 = Shock_bs2$simulation$wage_ds_t
net_balance_bs2 = xk_ds_bs2 - mk_ds_bs2
net_balance_bs2_ratio= (xk_ds_bs2 - mk_ds_bs2)/yk_ds_bs2

@@

test_gap_bs2= (wage_ds_t_bs2-max_dp_bs2)/ wage_ds_t_bs2

```{r}
plot(wage_ds_t_bs2, col= "black", xlab= "Year", ylab= "% Change in wages", main= "Targeted Wage Gap");
lines(wage_ds_t, col="red")
grid()

@@

yk_ds_02 = Shock_2$simulation$yk_ds
emp_02 = Shock_2$simulation$emp
wage_ds_02 = Shock_2$simulation$wage_ds
ur_ds_02 = Shock_2$simulation$ur_ds
pc_ds_02 = Shock_2$simulation$pc_ds
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
pconk_ds_02 = Shock_2$simulation$pconk_ds
komp_r_02 = Shock_2$simulation$komp_r
max_dp_02 = Shock_2$simulation$max_dp
nben_h_02 = Shock_2$simulation$nben_h
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
ik_02 = Shock_2$simulation$ik
wage_ds_t_02 = Shock_2$simulation$wage_ds_t
nben_h_un_02 = Shock_2$simulation$nben_h_un
nl_g_02 = Shock_2$simulation$nl_g
nsben_h_02 = Shock_2$simulation$nsben_h
dp_person_02 = Shock_2$simulation$dp_person
xk_ds_02 = Shock_2$simulation$xk_ds
mk_ds_02 = Shock_2$simulation$mk_ds
ik_02 = Shock_2$simulation$ik
rer_02 = Shock_2$simulation$rer
ps_ds_02 = Shock_2$simulation$ps_ds
i_bd_nfc_k_ds_02 = Shock_2$simulation$i_bd_nfc_k_ds
yd1_hk_ds_02 = Shock_2$simulation$yd1_hk_ds
yd2a_hk_ds_02 = Shock_2$simulation$yd2a_hk_ds
yd2b_hk_02 = Shock_2$simulation$yd2b_hk
i_equip_nfc_k_ds_02 = Shock_2$simulation$i_equip_nfc_k_ds
u_ds_02 = Shock_2$simulation$u_ds
wage_gap1_02 = Shock_2$simulation$wage_gap1
gk_02 = Shock_2$simulation$gk
kont_h_ratio_02 = Shock_2$simulation$kont_h_ratio
lf_02 = Shock_2$simulation$lf
wage_gap_02 = Shock_2$simulation$wage_gap
max_gap_02 = Shock_2$simulation$max_gap
unemp_02 = Shock_2$simulation$unemp
inflation_02 = Shock_2$simulation$inflation
prod_02 = Shock_2$simulation$prod
ws_02 = Shock_2$simulation$ws
net_balance_02 = xk_ds_02 - mk_ds_02

test_gap_02= (wage_ds_t_02-max_dp_02)/ wage_ds_t_02
```

```{r, fig.width=12, fig.height=5}
par(mfrow=c(1,2))

plot(wage_gap1_bs2, col= "black", xlab= "Year", ylab= "Wage gap (ratio)", main= "Wage Gap in baseline");
lines(wage_gap1_00, col= "red");
legend("top",legend=c("Baseline with wage channel", "Baseline without wage channel"),lty=c(1,1),lwd=c(2),bty="n", col = c("black", "red"));
grid()

plot(wage_ds_bs2, col= "black", xlab= "Year", ylab= "Wages (level)", main= "Wages in baseline");
lines(wage_ds_00, col= "red");
legend("top",legend=c("Baseline with wage channel", "Baseline without wage channel"),lty=c(1,1),lwd=c(2),bty="n", col = c("black", "red"));
grid()

@@

```{r, fig.width=10, fig.height=5}

par(mfrow=c(1,2))
plot(wage_gap1_bs2, col= "black", xlab= "Year", ylab= "Ratio", main= "Wage gaps baseline");
lines(test_gap_bs2, col="red");
legend("top",legend=c("Wage_gap (wages)", "Wage_gap (targeted wages)"),lty=c(1,1),lwd=c(2),bty="n", col = c("black", "red"));
grid()

plot(wage_gap1_02, col= "black", xlab= "Year", ylab= "Ratio", main= "Wage gaps shock");
lines(test_gap_02, col="red");
legend("top",legend=c("Wage_gap (wages)", "Wage_gap (targeted wages)"),lty=c(1,1),lwd=c(2),bty="n", col = c("black", "red"));
grid()
